---
title: "R Notebook"
output: html_notebook
---


Uebungsblatt e. Teil b.
Dauren Tursynbek 108019256321


Aufgabe 8.

```{r}
data(mtcars)
res = lm(mpg ~ factor(cyl) + factor(am), data=mtcars)
summary(res)
```

```{r}
interaction.plot(mtcars$cyl, mtcars$am, mtcars$mpg)
```

```{r}

```


Aufgabe 9.

```{r}
resWW = lm(len ~ supp*dose, data=ToothGrowth)
summary(resWW)
res = lm(len ~ supp+dose, data=ToothGrowth)
summary(res)
anova(res, resWW)
```


Aufgabe 10.

```{r}
attach(fat)
res=lm(body.fat ~ age+weight+height+BMI+neck+chest+abdomen+hip+thigh+knee+ankle+bicep+forearm+wrist)
stepAIC(res)
detach(fat)
```

Aufgabe 11.

```{r}
res = matrix(0, nrow = 200, ncol = 2)
for(i in 1:200) {
  x = rep(1:10, 4)
  y = rnorm(40, 1 + 2*x, 3)
  res[i,] = coef(lm(y ~ x))
}
plot(res[, 1], res[, 2])
```








Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
